### 2021-10-27 documentos/math.tex
<!DOCTYPE html><html><head><title>Unable to Connect</title><style type="text/css">*{font-family: "Open Sans", sans-serif; color: rgb(101, 102, 106)}body{padding-left: 50px; background-color: #f7f7f7;}h1{font-size: 48px; font-weight: 100; letter-spacing: 0.025em}h2{font-size: 28px; font-weight: 100; letter-spacing: 0.01em}p{font-size: 13px; font-weight: 300; letter-spacing: 0.08em line-height: 1.4;}</style></head><body><h1>Error accessing site</h1><h2>Unable to Connect</h2><p>The requested site&#39;s DNS address could not be found.</p></body></html>
Updated build targets.

\section{Mathematical considerations} 
\subsection{Diagonalization of Choi matrix}

% Intro {{{
Prueba de la $\sa$ \todo{Alejo escribe esta parte. Dejelo aca todo y luego si acaso 
pasamos cosas al apendice. Caso general}

This part is devoted to derive the set of conditions a Pauli map need to
satisfy to fulfill the CP condition i.e. all the eigenvalues of the Choi matrix
associated to the channel must be non-negative. First we obtain the set of
inequalities for a single qubit Pauli channel and then we extend the results
for the general case of $N$ qubits.

% }}}
\subsubsection{Single qubit Pauli channels} % {{{

\afnote{Notación para matrices densidad vectorizadas? $\varrho$ ?}
\janote{Qué tal $\vec\rho\quad$?}
\afnote{Por ahora uso este $\kket{\rho}$}

We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\alpha}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel. By writing the density matrix in vector form $\kket{\rho}=2^{-1}\sum_{\alpha=0}^{3} r_{\alpha} \kket{\sigma_{\alpha}}$, the matrix form of the map $\mathcal{E}$ may be written as
% 
\begin{equation}
\hat{\mathcal{E}} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \ddyada{\sigma_{\alpha}},
% \label{Map_Pauli}
\end{equation}
%
where the kets $\kket{\sigma_{\alpha}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \bbrakket{{\sigma_{\alpha} }}{{\sigma_{\alpha'} }} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$. After some steps it is possible to show that the associated Choi matrix reads
% 
\begin{equation}
 \mathcal{D} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \sigma_{\alpha} \otimes \sigma_{\alpha}^*.
%  \label{Choi_1}
\end{equation}
% 
Moreover, observe that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel, with Kraus operators given by $K_{\alpha}=\sqrt{\tau_{\alpha}/2}\sigma_{\alpha}$ \cite{CHRUSCINSKI20131425}. In this way the Choi matrix $\mathcal{D}$ is diagonal in the Pauli basis (see Appendix for details),
%
\begin{equation}
 \mathcal{D} \kket{\sigma_{\alpha}}= \lambda_{\alpha} \kket{\sigma_{\alpha}},
\end{equation}
% 
with eigenvalues given by 
% 
\begin{equation}
 \lambda_{\alpha} = \sum_{\beta=0}^3\sa_{\alpha\beta}\tau_{\beta},
\end{equation}
%
or more compactly $\vec{\lambda} = \sa~\vec{\tau}$, where $\sa=2^{-1}H\otimes
H$ and $H$ is the Hadamard matrix,
\cpnote{Decidir si se usa esa $a$ o la otra para ser consistente con lo de los 
generadores}
%
\begin{equation}
 H=\begin{pmatrix}
        1 & 1\\
        1 & -1\\
    \end{pmatrix}.
 \label{Hadd_Mat}
\end{equation}

\cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar y la
dejo por aca por si se nos ofrece}
\begin{equation}
\sa=\left(
\begin{array}{cccc}
1 &1 &1   &1   \\
 1 & 1  & -1&-1   \\
1  & -1  & 1 & -1\\
1&-1&-1&1  
\end{array}
\right)=\frac12\sa^{-1}.
\label{eq:1}
\end{equation}
% 
%  }}}
\subsubsection{$N$ qubits} % {{{
% 
Analogously to the single qubit case, one can define the $N$-qubits Pauli map $\mathcal{E}_N$
% 
\begin{equation}
\rho \to \rho'=\mathcal{E}_N[\rho ]=\frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
% \label{Pauli_Map}
\end{equation}
% 
with $-1\leq \tau_{\vec{\alpha}} \leq 1$. 
% 
In this case the density matrix in vector form holds 
% 
\begin{equation}
 \kket{\rho}=\frac{1}{2^N}\sum_{\vec{\alpha}} r_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
\end{equation}
where $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\dots
\otimes\kket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation
$\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} = \tr
\left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N
~\delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of this map is
given by
\begin{equation}
\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} \ddyada{\sigma_{\vec{\alpha} }}.
% \label{Map_Pauli}
\end{equation}
As in the previous case, the Choi matrix $\mathcal{D}_N$ may be written in terms of tensor products of Pauli matrices
\begin{equation}
 \mathcal{D}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}}  \bigotimes_{j=1}^N \sigma_{\alpha_j} \otimes \sigma_{\alpha_j}^*.
%  \label{Choi_1}
\end{equation}
After several steps, it is possible to prove that analogously to the single qubit case, $\mathcal{D}_N$ is diagonal in the $N$-qubits Pauli basis
\begin{equation}
 \mathcal{D}_N \kket{\sigma_{\vec{\alpha} }}
   = \lambda_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
\end{equation}
with eigenvalues $\lambda_{\vec{\alpha}}$ given by 
\begin{equation}
 \lambda_{\valpha} = \sum_{\vbeta} \san_{\valpha\vbeta}\tau_{\vbeta},
\label{eq:lambda:is:A:tau}
\end{equation}
where 
\begin{equation}
 \san=\sa^{\otimes N}
% =\frac{1}{2^N}\left(H\otimes H\right)^{\otimes N}=\left(\frac{H}{\sqrt{2}}\right)^{\otimes 2N}.
\end{equation}
Again, the proofs are provided in appendix \ref{sec:appendix:diagonalization}
\cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar para $N$ 
qubits.}
% (Proofs in an appendix using binary indices XD)
% }}}

>>>>

\section{Mathematical considerations} 
This section is devoted to derive the conditions a Pauli map need to
satisfy to fulfill the CP condition i.e. that all the eigenvalues of the Choi matrix
associated to the channel must be non-negative. 
To do so, we first calculate and diagonalize the matrix associated with the map, 
first for a single qubit and then for $N$ qubits. We then associate a vector space
to the set of coefficients $\{\tau_\valpha\}$ in \eref{eq:PCE_definition}, from 
which we are able to derive several important conclusions.

% First we obtain the set of
% inequalities for a single qubit Pauli channel and then we extend the results
% for the general case of $N$ qubits. 
\subsection{Diagonalization of Choi matrix}

\subsubsection{Single qubit Pauli channels} % {{{

% \afnote{Notación para matrices densidad vectorizadas? $\varrho$ ?}
% \janote{Qué tal $\vec\rho\quad$?}
% \afnote{Por ahora uso este $\kket{\rho}$}

We now study the matrix form of the single qubit map $\mathcal{E}$ in
order to construct the associated Choi matrix. 
% and the conditions the set of parameters
% $\{\tau_{\alpha}\}$ need to satisfy in order to $\mathcal{E}$ be considered a
% quantum channel. 
To do so, we shall denote operators in the superoperator space with the symbol
$\kket{\cdot}$. For example, $\kket{\sigma_{\alpha}}$ correspond to the
vectorized elements of the Pauli basis and satisfy the usual relation 
$\bbrakket{{\sigma_{\alpha}}}{{\sigma_{\alpha'} }} = \tr
\left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2
\delta_{\alpha\alpha'}$.
In this language, 
the state reads
$\kket{\rho}=2^{-1}\sum_{\alpha=0}^{3} r_{\alpha} \kket{\sigma_{\alpha}}$
and the 
% By writing the density matrix in vector form
% $\kket{\rho}=2^{-1}\sum_{\alpha=0}^{3} r_{\alpha} \kket{\sigma_{\alpha}}$, the
matrix form of the map $\mathcal{E}$ is
% 
\begin{equation}
\hat{\mathcal{E}} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha}
\ddyada{\sigma_{\alpha}}.
% \label{Map_Pauli}
\end{equation}
%
% where the kets $\kket{\sigma_{\alpha}}$ correspond to the vectorized elements
% of the Pauli basis and satisfy the usual relation $ \bbrakket{{\sigma_{\alpha}
% }}{{\sigma_{\alpha'} }} = \tr \left(\sigma_{\alpha}^{\dagger}
% \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$. 
After some steps it is possible to show that the associated Choi matrix reads
% 
\begin{equation}
 \mathcal{D} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \sigma_{\alpha} \otimes \sigma_{\alpha}^*.
%  \label{Choi_1}
\end{equation}
% 
Moreover, observe that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel, with Kraus operators given by $K_{\alpha}=\sqrt{\tau_{\alpha}/2}\sigma_{\alpha}$ \cite{CHRUSCINSKI20131425}. In this way the Choi matrix $\mathcal{D}$ is diagonal in the Pauli basis (see Appendix for details),
%
\begin{equation}
 \mathcal{D} \kket{\sigma_{\alpha}}= \lambda_{\alpha} \kket{\sigma_{\alpha}},
\end{equation}
% 
with eigenvalues given by 
\begin{equation}
 \lambda_{\alpha} = \frac12 \sum_{\beta=0}^3\sa_{\alpha\beta}\tau_{\beta},
\end{equation}
or more compactly $\vec{\lambda} = \sa \vec{\tau}$, where 
\begin{equation}
\sa=\left(
\begin{array}{cccc}
1 &1 &1   &1   \\
 1 & 1  & -1&-1   \\
1  & -1  & 1 & -1\\
1&-1&-1&1  
\end{array}
\right)
% =\frac12\sa^{-1}.
\label{eq:1}
\end{equation}

% $\sa=2^{-1}H\otimes H$ and $H$ is the Hadamard matrix,
% \cpnote{Decidir si se usa esa $a$ o la otra para ser consistente con lo de los 
% generadores}
% %
% \begin{equation}
%  H=\begin{pmatrix}
%         1 & 1\\
%         1 & -1\\
%     \end{pmatrix}.
%  \label{Hadd_Mat}
% \end{equation}

\cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar y la
dejo por aca por si se nos ofrece}
% 
%  }}}
\subsubsection{$N$ qubits} % {{{
% 
Analogously to the single qubit case, one can define the $N$-qubits Pauli map $\mathcal{E}_N$
% 
\begin{equation}
\rho \to \rho'=\mathcal{E}_N[\rho ]=\frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
% \label{Pauli_Map}
\end{equation}
% 
with $-1\leq \tau_{\vec{\alpha}} \leq 1$. 
% 
In this case the density matrix in vector form holds 
% 
\begin{equation}
 \kket{\rho}=\frac{1}{2^N}\sum_{\vec{\alpha}} r_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
\end{equation}
where $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\dots
\otimes\kket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation
$\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} = \tr
\left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N
~\delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of this map is
given by
\begin{equation}
\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} \ddyada{\sigma_{\vec{\alpha} }}.
% \label{Map_Pauli}
\end{equation}
As in the previous case, the Choi matrix $\mathcal{D}_N$ may be written in terms of tensor products of Pauli matrices
\begin{equation}
 \mathcal{D}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}}  \bigotimes_{j=1}^N \sigma_{\alpha_j} \otimes \sigma_{\alpha_j}^*.
%  \label{Choi_1}
\end{equation}
After several steps, it is possible to prove that analogously to the single qubit case, $\mathcal{D}_N$ is diagonal in the $N$-qubits Pauli basis
\begin{equation}
 \mathcal{D}_N \kket{\sigma_{\vec{\alpha} }}
   = \lambda_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
\end{equation}
with eigenvalues $\lambda_{\vec{\alpha}}$ given by 
\begin{equation}
 \lambda_{\valpha} = \frac{1}{2^N} \sum_{\vbeta} \san_{\valpha\vbeta}\tau_{\vbeta},
\label{eq:lambda:is:A:tau}
\end{equation}
where 
\begin{equation}
 \san=\sa^{\otimes N}
% =\frac{1}{2^N}\left(H\otimes H\right)^{\otimes N}=\left(\frac{H}{\sqrt{2}}\right)^{\otimes 2N}.
\end{equation}
Again, the proofs are provided in appendix \ref{sec:appendix:diagonalization}
\cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar para $N$ 
qubits.}
% (Proofs in an appendix using binary indices XD)
% }}}
